Advantages of mixed unitary operators for quantum information processing

### 2019-02-22 decorrelation/mixed_unitaries.tex
Rigedits

The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016}, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum advantage milestone \cite{1203.5813} has yet to be definitively reached. The limiting factor, of course, is errors in the quantum gate operations.

The impact of an error in a quantum gate depends strongly on both the magnitude and the nature of the errors. Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations that induce repeatable, undesired unitary errors on the state of a QIP. Errors of this type are correlated in time and add up coherently. They are are  computationally expensive to model and it is difficult to place tight analytic bounds on circuit performance. Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment. Systems with stochastic errors can be  modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips. These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate.

Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs. While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict. The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors. For long circuits, this can add up extremely quickly. Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates. The resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.

@@

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mathematical preliminaries}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context\cite{1810.05651}, then we can usually describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.  When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma),
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. The action of a gate is then given by the usual matrix multiplication:
\begin{equation}\label{error_def}
  \vec\rho \rightarrow \target\vec\rho = \error \actual \vec\rho.
\end{equation}
Here $\target$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel:

@@

In general, if we have a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results from drawing from the controls probabilistically has elements given by:
\begin{align}
	\mathcal{M}_{jk} 
		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
\end{align}
The first term corresponds to the identity, and $\sin\theta_i^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta_i\cos\theta_i$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term. The result would be a purely stochastic channel.

The problem of minimizing the last term:
\begin{equation}
\sum_i\sin\theta_i\cos\theta_i(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)
\end{equation}
 can equivalently be cast as trying to construct a family of vectors whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).

@@

A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.  The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$. From this definition, we can use linearity to compute the AGI of a MUP. We see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting. The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MUP than any of the processes being mixed.

@@

% ==============================================================================
% Section: Constructing Useful Unitary Processes
% ==============================================================================
\section{Constructing Useful Unitary Processes}
\label{sec:mixed_unitary_processes}
\subsection{Simple Example}
\label{sec:simple_example}
There are often many possible ways of implementing any given target quantum gate. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} As a simple example, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis. The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$. Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.

@@

In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic. Such a channel could be constructed, for instance, by drawing from this collection uniformly at random. More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}. We implemented such a routine on a superconducting qubit.
% ==============================================================================
% Section: Experimental Results
% ==============================================================================

\subsection{Experimental Implementation}
\label{sec:experimental_results}
Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit. In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}. To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.

As discussed in the previous section, we chose here to minimize the off diagonal elements of the process matrix. To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process. We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$. In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses. In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors. The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$. Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses. 
\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{rb_data.pdf}
  \caption{Randomized benchmarking experiments ran using different pulse definitions. The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the MUP.}
  \label{fig:rb}
\end{figure}

Additionally, by minimizing the off-diagonal elements of the process matrix, we expect to produce a process with minimal coherent error. To see that this is the case, we cite the results in \cite{Ball2016}. For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length. On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length. We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables. Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.

\subsection{Diamond Norm Minimization}
\label{sec:small_diamond_norm}
If our primary goal is for our MUP to have increased performance, then a useful target for constructing MUPs is instead minimizing the diamond norm. As in Section \ref{sec:simple_example}, the MUP that minimizes the diamond norm has matrix elements given by:
\begin{equation}\label{eq:balanced}
\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
\end{equation}
This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$. Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$. While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application. However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j H_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MUP with this property. Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MUP with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations. In these situations, one can equivantly use convex optimization to solve this problem. Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e. for $m$, $n\times n$ Hamiltonians:
\begin{equation}\label{eq:vectorized_hamiltonians}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{m_{11}} &  &  H_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MUP is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one. This forms a convex optimization problem, and can be written as:

@@

\subsection{Robustly Mixed Unitary Processes}
\label{sec:robustly_mixed}

While mixed unitary processes offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MUP will degrade. Thus, we would like to design MUPs that are \textit{robust} to this drift. To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}. Instead of only requiring that the $0^{th}$ derivative averages to zero, we will impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
We say that a mixed unitary process is robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq k \leq \ell$:
\begin{equation}\label{eq:MUP}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
\end{gathered}
\end{equation}
In particular, we see that a 0MUP satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MUP as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MUP will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MUP} as:
\begin{equation}\label{eq:MUP-relaxed}
\begin{gathered}
\sum\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MUP. Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MUP.

@@

% ==============================================================================
% Section: Numerical Results
% ==============================================================================
\subsection{Numerical Implementation}
\label{sec:numerical_results}
\label{one_qubit_performance}
In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
\begin{equation}\label{eq:1Qham}
  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
\end{equation}
We use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls. In our implementation, we modify the gradient so that we find controls that perform well in a Gaussian weighted neighborhood, with a standard deviation of $\sigma=.001$. We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal. Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMUP}. These results demonstrate several properties that make MUPs both useful and tractable.

>>>>

The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016}, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached. The limiting factor, of course, is errors in the quantum gate operations.

The impact of an error in a quantum gate depends strongly on both the magnitude and the nature of the errors. Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations that induce repeatable, undesired unitary errors on the state of a QIP. Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit. They are are  computationally expensive to model and it can be difficult to place tight analytic bounds on circuit performance. Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment. Systems with stochastic errors can be  modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips. These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate [Ken Brown, Steve Flammia].

Quantitative bounds on the performance of quantum circuits can be constructed using the diamond distance []. \note{Discuss subadditivity of diamond norm here... The resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates. While these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict. The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors. For long circuits, this can add up extremely quickly. 
}. 
Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs. Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.

@@

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mathematical preliminaries}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context\cite{1810.05651}, then we can usually describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.  When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma)/2^n,
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. For a single qubit, this is $\vec\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}$.  The action of a gate is then given by the usual matrix multiplication:
\begin{equation}\label{error_def}
  \vec\rho \rightarrow \target\vec\rho = \error \actual \vec\rho.
\end{equation}
Here $\target$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel:

@@

\note{this should go somewhere:}
There are often many possible ways of implementing any given target quantum gate. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011}

@@

\note{fix this} A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.  The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$. From this definition, we can use linearity to compute the AGI of a MUP. We see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting. The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MUP than any of the processes being mixed.

@@

\subsection{A simple example}
\label{sec:simple_example}
As a simple example, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis. The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$. Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.

In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic. Such a channel could be constructed, for instance, by drawing from this collection uniformly at random. More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}. We implemented such a routine on a superconducting qubit.

The error operator corresponding to a rotation error by angle $\epsilon$ is then:
\begin{equation}
\error(\epsilon) =
	\left(\begin{array}{ccccc}
		1 & 0 & 0 & 0 \\ 
		0 & \cos\epsilon & \sin\epsilon  & 0  \\
		0 & -\sin\epsilon & \cos\epsilon & 0  \\
		0 & 0 & 0 & 1
	\end{array} 	
	\right)
\end{equation}
\note{Don't be dumb with right hand rules}
The associated diamond distance of this channel is $\abs{\mathcal{I} - \error(\epsilon)}_\diamond \simeq \epsilon$, while the fidelity of the channel is $\mathcal{F}(\error(\epsilon)) = \epsilon^2$. If we were construct two channels, one with error $\error(\epsilon)$ and one with error $\error(-\epsilon)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\epsilon) + \error(\epsilon)\right)$. The effective channel then has a matrix representation:
\begin{equation}
	\error(\epsilon) =
	\left(\begin{array}{ccccc}
		1 & 0 & 0 & 0 \\ 
		0 & \cos\epsilon & 0  & 0  \\
		0 & 0 & \cos\epsilon & 0  \\
		0 & 0 & 0 & 1
	\end{array} 	
	\right) \simeq \mathcal{I} - 
	\left(\begin{array}{ccccc}
		0 & 0 & 0 & 0 \\ 
		0 & \epsilon^2/2 & 0  & 0  \\
		0 & 0 & \epsilon^2/2 & 0  \\
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}
And with same average process fidelity, $\epsilon^2$, but now a suppressed diamond norm $\epsilon^2$. Now write this in terms of the error generators $\error(\epsilon) = \exp(\epsilon G)$ where
\begin{equation}
	G =
	\left(\begin{array}{ccccc}
		0 & 0 & 0 & 0 \\ 
		0 & 0 & 1  & 0  \\
		0 & -1 & 0 & 0  \\
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}
The effective generator vanishes at first order.

\begin{equation}
	\error(\epsilon) = \mathcal{I} + \epsilon G + \frac{1}{2}\epsilon^2 G^2 + \mathcal{O}(\epsilon^3)
\end{equation}
\begin{align}
	\error_{\text{eff}} 
		% &= \sum_i \omega_i \error_i \\
		% &= \sum_i \omega_i \left(\mathcal{I} + \epsilon_i G_i + \frac{1}{2}\epsilon_i^2 G_i^2 + \cdots \right) \\
		&= \mathcal{I} + \sum_i \omega_i \epsilon_i G_i+ \sum_i \omega_i \frac{1}{2}\epsilon^2_i G_i^2 + + \mathcal{O}(\epsilon^3)
\end{align}
\begin{equation}
	\error_{\text{eff}} = \mathcal{I} + \sum_i \omega_i \frac{1}{2}\epsilon^2_i G_i^2 + \mathcal{O}(\epsilon^3)
\end{equation}

@@

Alternatively, \note{Draw box around the (2,4),(2,3),(3,4) elements of the G matrix}. We can then eliminate off diagonal entries, resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable. \note{more here about alternative method. Also discuss Fig 2.}.

\note{END}

% In general, if we have a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results from drawing from the controls probabilistically has elements given by:
% \begin{align}
% 	\mathcal{M}_{jk} 
% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
% 		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
% 		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
% \end{align}
% The first term corresponds to the identity, and $\sin\theta_i^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta_i\cos\theta_i$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term. The result would be a purely stochastic channel.

% The problem of minimizing the last term:
% \begin{equation}
% \sum_i\sin\theta_i\cos\theta_i(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)
% \end{equation}
%  can equivalently be cast as trying to construct a family of vectors whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).

% ==============================================================================
% Section: Constructing Useful Unitary Processes
% ==============================================================================
\section{Constructing Useful Unitary Processes}
\label{sec:mixed_unitary_processes}
\note{write an introduction to this section here} 
In general, we want to construct a problem so that 0 is in the convex hull of some set of vectors. These vectors might represent the off-diagonal elements of the error maps, or they could be the error generator. As we'll see in section ... we could also include the derivatives with respect to various parameters. With appropriate weighting, we could minimize any number of effects. Which optimization we choose will depend on the approach. \note{Then go into examples below. }

% ==============================================================================
% Section: Generators
% ==============================================================================

\subsection{First-order generators} % (fold)
\label{sub:first_order_generators}
\note{say that we are linearizing the diamond distance calculation -  rewrite this whole thing}
If our primary goal is for our MUP to have increased performance, then a useful target for constructing MUPs is instead minimizing the diamond norm. As in Section \ref{sec:simple_example}, the MUP that minimizes the diamond norm has matrix elements given by:
\begin{equation}\label{eq:balanced}
\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
\end{equation}
This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$. Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$. While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application. However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j H_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MUP with this property. Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MUP with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations. In these situations, one can equivantly use convex optimization to solve this problem. Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e. for $m$, $n\times n$ Hamiltonians:
\begin{equation}\label{eq:vectorized_hamiltonians}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{m_{11}} &  &  H_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MUP is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one. This forms a convex optimization problem, and can be written as:

@@

% subsection first_order_generators (end)

% ==============================================================================
% Section: Off-diagonals
% ==============================================================================

\subsection{Off-diagonals} % (fold)
\label{sub:off_diagonals}

% subsection off_diagonals (end)

% ==============================================================================
% Section: Robustness
% ==============================================================================

\subsection{Adding robustness} % (fold)
\label{sub:adding_robustness}
\note{this section is a little bit heavy on the notation - is there anything we can do to ease that? Perhaps in the introduction we can specify the problem a little more clearly and then this can be just a restriction of that general model }
While mixed unitary processes offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MUP will degrade. Thus, we would like to design MUPs that are \textit{robust} to this drift. To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}. Instead of only requiring that the $0^{th}$ derivative averages to zero, we will impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
We say that a mixed unitary process is robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq k \leq \ell$:
\begin{equation}\label{eq:MUP}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
\end{gathered}
\end{equation}
In particular, we see that a 0MUP satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MUP as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MUP will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MUP} as:
\begin{equation}\label{eq:MUP-relaxed}
\begin{gathered}
\sum\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MUP. Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MUP.

@@

% subsection adding_robustness (end)

% ==============================================================================
% Section: Norm regularization
% ==============================================================================

% ==============================================================================
% Section: Sparsity
% ==============================================================================

\section{Results} % (fold)
\label{sec:results}

% ==============================================================================
% Section: Experimental Results
% ==============================================================================

\subsection{Experimental} % (fold)
\label{sub:experimental}
Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit. In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}. To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
